Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-18 paper/paper.tex
moved Rui's newcommand from paper to macros, changed color
pass

\newcommand\rui[1]{\nb{Rui}{blue}{#1}}

@@

Figure~\ref{fig:pingscan-example} \rui{any reason for the bolds?} shows a Suricata rule that captures
Ping Scan, as documented on NMAP~\cite{netmap}, a network security
auditing tool. The essential options to capture the attack are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

>>>>

@@

Figure~\ref{fig:pingscan-example} \rui{any reason for the bolds?} \Luc{these are
the options that are important for detection, the other ones are documentation
options} shows a Suricata rule that captures
Ping Scan, as documented on NMAP~\cite{netmap}, a network security
auditing tool. The essential options to capture the attack are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.
